Unsupervised embeddings of organizations capture latent structure of scientific mobility

### 2020-04-10 paper/current/main.tex

Then, we can rewrite Eq.~\ref{eq:gravity_model} as,
\begin{equation}
   \frac{T_{ij}}{\mu_{i} \mu_{j}} \propto \exp(\cos(v_i,v_j))
\end{equation}

%
% Figure - Conditional Probability
%
\begin{figure}
    \centering
    \includegraphics[width=0.8\columnwidth]{\figdir/Math/use_all_log.pdf}
    \caption{
    \textbf{a}.   Relationship between $M_i$ and $\mu_i$.
    \textbf{b}.   Relationship between the conditional probability $p(j|i)$, Eq. \ref{eq:flux_conditional_prob} which is measured in the data and approximate functional form Eq. \ref{eq:real_embedding_relationship}}.
    \label{fig:math_part}
\end{figure}

>>>>

It can be checked in Fig.\ref{fig:math_part}. With this approximation, we can rewrite Eq.~\ref{eq:gravity_model} as,
\begin{equation}
   \frac{T_{ij}}{\mu_{i} \mu_{j}} \propto \exp(\cos(v_i,v_j))
\end{equation}

%
% Figure - Conditional Probability
%
\begin{figure}
    \centering
    \includegraphics[width=0.4\columnwidth]{\figdir/Math/m_and_M.pdf}
    \caption{
    Relationship between $M_i$ and $\mu_i$.}.
    \label{fig:math_part}
\end{figure}
